Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-01-15 paper/paper.tex
clean up figure 2

\includegraphics[width=\linewidth, trim={0in 0.7in 0 0.05in}, clip=true]{figs/effects_histogram.pdf}

\includegraphics[width=\linewidth, trim={0in 0.36in 0 0in}, clip=true]{figs/effects_dist.pdf}
\caption{
Distribution of effects of different types of mutations.
{\bf (A)}
Histograms of effects of synonymous, nonsynonymous, and stop-codon mutations across all viral genes.
Neutral mutations have effects of zero, and deleterious mutations have negative effects.
\jdbcomment{Maybe add dotted vertical line at zero to denote neutrality?}
{\bf (B)}
Effects of each type of mutation for each viral gene.
Dark squares indicate the median effect, and the lighter rectangles span the interquartile range.
Mutation types are color-coded as in panel A.
Both panels show only mutations with expected counts of at least 20.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_histogram.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_dist.html} for interactive versions of these plots that allow adjustment of the expected-count cutoff and other options (such as separate histograms for each gene).
\label{fig:effects_dist}
}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figs/fig2.pdf}
\caption{
Distribution of effects of different types of mutations.
{\bf (A)}
Histograms of effects of synonymous, nonsynonymous, and stop-codon mutations across all viral genes.
Neutral mutations have effects of zero (dashed gray vertical lines), and deleterious mutations have negative effects.
{\bf (B)}
Effects of each type of mutation for each viral gene.
Dark squares indicate the median effect, and the lighter rectangles span the interquartile range.
Mutation types are color-coded as in panel A.
Both panels show only mutations with expected counts of at least 10.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_histogram.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_dist.html} for interactive versions of these plots that allow adjustment of the expected-count cutoff and other options (such as separate histograms for each gene).
\label{fig:effects_dist}
}
\end{figure*}
